Pillar 1 - Sequential Pattern Mining

### 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
previously taken courses per student per period

```{r}

>>>>

### Preceding courses
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    Cumulative_transcript=lag(Reduce(paste, item, accumulate=T)),
    Cumulative_transcript= str_split(Cumulative_transcript," ")
                                     )
```

###Computing probabilities
```{r}
